---
title: "Xaringan presentation"
subtitle: "With a GSU Flavor"
author: "Josh Allen"
institute: 
 - "Deparment of Political Science"
 -  "Georgia State University"
date: "2016/12/12 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: ["gsu-css/gsu.css", "gsu-css/gsu-fonts.css"]
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE, htmltools.preserve.raw = FALSE)
```

# Xaringan presentation

## What is Xaringan?

- [`Xaringan`](https://github.com/yihui/xaringan) is an R package that can be used to create slides

- The name comes from Sharingan from the anime Naruto! `r emo::ji("laugh")`

- How to install:

```{r eval=FALSE, include=TRUE}
devtools::install_github('yihui/xaringan')
```

- How to get started:

    - [Xaringan github](https://github.com/yihui/xaringan)

---
# Xaringan presentation

- Here are some great tutorials:

  - [Xaringan github](https://github.com/yihui/xaringan)

  - [Yihui's tutorial](https://slides.yihui.org/xaringan/#1)
  
  - [Making Slides in the Tada!-verse](https://apreshill.github.io/data-vis-labs-2018/slides/06-slides_xaringan.html#1)
  
  - [Making slides in R Markdown](http://arm.rbind.io/slides/xaringan.html#1)

- Some useful extensions for `Xaringan`

  - [`xaringanExtra` R package](https://github.com/gadenbuie/xaringanExtra)
  
  - [`xaringanthemer` R packge](https://pkg.garrickadenbuie.com/xaringanthemer/index.html)
  
  - [Xaringan Gallery](https://xaringan.gallery/)
  
  - [`DT` R package for interactive tables](https://rstudio.github.io/DT/)


---
# GSU theme

- How to enable the gsu theme:

```md
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: ["gsu", "gsu-fonts"]
```

- The GSU theme for `Xaringan` presentation is suitable to work with a 16:9 aspect ratio

```md
nature:
  highlightStyle: github
  highlightLines: true
  countIncrementalSlides: false
  ratio: "16:9"
```

---
# gsu-Madison theme

- We can make `blockquotes` by calling `<gsu-blockquote>some texts</gsu-blockquote>`

<gsu-blockquote>This is a blocked quote</gsu-blockquote> 

- Highlight text using `**text**` like **this**

- Italic text using `*text*` like *this*

- Bold text using `.bold[text]` like .bold[text]

---
# GSU theme

- We can change the color of any text by using `.color[text]`. I prepared three color palettes for the users. 

  - [GSU palette](https://brand.wisc.edu/web/colors/): `.gsu-blue[text]`,`.gsu-dark[text]`,`.gsu-gray-blue[text]`,`.gsu-gray-darker[text]`, `.gsu-gray-darkest[text]`, `.gsu-anchor-color[text]`
  - .gsu-blue[gsu blue], .gsu-dark[gsu dark], .gsu-gray-blue[gsu gray blue], .gsu-gray-darker[gsu gray darker], .gsu-gray-darkest[gsu gray darkest], .gsu-anchor-color[gsu anchor]

  - Palette 1: `.p1-yellow[text]`, `.p1-orange[text]`, `.p1-darkred[text]`, `.p1-purple[text]`
  - .p1-yellow[text], .p1-orange[text], .p1-darkred[text], .p1-purple[text]
  
  - Palette 2: `.p2-green[text]`, `.p2-blue[text]`, `.p2-yellow[text]`, `.p2-red[text]`
  - .p2-green[text], .p2-blue[text], .p2-yellow[text], .p2-red[text]


---
class: bold-last-item

# GSU theme

- add `class: bold-last-item` at the beginning of each slide to switch on the **Bold-Last-Item**

```css
---
class: bold-last-item
```
--
- For example
--
- Bullet list 1
--
- Bullet list 2
--
- Bullet list 3
---
class: highlight-last-item
# GSU theme
- add `class: highlight-last-item` at the beginning of each slide to switch on the **Highlight-Last-Item**
--
- For example
--
- Bullet list 1
--
- Bullet list 2
--
- Bullet list 3
---
```{r xaringan-extra-styles, echo=FALSE}
xaringanExtra::use_extra_styles(
  hover_code_line = TRUE,         #<<
  mute_unhighlighted_code = TRUE  #<<
)
```
# R code and plot output

```{r, fig.height=4.5, fig.width=9, fig.retina=2, fig.align='center', message=FALSE, warning=FALSE}
library("tidyverse")
cars %>% 
  ggplot(aes(x = dist, y = speed)) + 
  geom_point() + 
  geom_smooth(method = 'lm', formula = y ~ poly(x, 2)) + 
  theme_bw(base_size = 24) 
```

---
# Some Tips

- Do not forget to try the option **`yolo: true`** under **`xaringan::moon_reader`** in the YAML metadata of your R Markdown document. A picture of smiling Karl will be randomly insert in the slides.

- Use [`DT`](https://rstudio.github.io/DT/) for interactive tables.

- [`xaringanExtra` R package](https://github.com/gadenbuie/xaringanExtra) has many other additional and powerful features.

- Insert emoji by using [`emo`](https://github.com/hadley/emo) R package `r emo::ji("thinking")` `r emo::ji("laugh")` `r emo::ji("+1")`



- If you don't like the default font size and color, you can change them by using html syntax `<span style='font-size:55pt; color:#cc0033'> some text! </span>`

- If you want to change any elements of this theme, feel free to edit the source file as you like.

- The best way to learn about `Xaringan` is reading other people's source codes.

---