---
title: "Xaringan presentation"
subtitle: "With a GSU Flavor"
author: "Josh Allen"
institute: 
 - "Deparment of Political Science"
 -  "Georgia State University"
date: "2016/12/12 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: ["gsu-css/gsu.css", "gsu-css/gsu-fonts.css"]
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE, htmltools.preserve.raw = FALSE)
```

# Xaringan presentation

## What is Xaringan?

- [`Xaringan`](https://github.com/yihui/xaringan) is an R package that can be used to create slides

- The name comes from Sharingan from the anime Naruto! `r emo::ji("laugh")`

- How to install:

```{r eval=FALSE, include=TRUE}
devtools::install_github('yihui/xaringan')
```

- How to get started:

    - [Xaringan github](https://github.com/yihui/xaringan)

---
# Xaringan presentation

- Here are some great tutorials:

  - [Xaringan github](https://github.com/yihui/xaringan)

  - [Yihui's tutorial](https://slides.yihui.org/xaringan/#1)
  
  - [Making Slides in the Tada!-verse](https://apreshill.github.io/data-vis-labs-2018/slides/06-slides_xaringan.html#1)
  
  - [Making slides in R Markdown](http://arm.rbind.io/slides/xaringan.html#1)

- Some useful extensions for `Xaringan`

  - [`xaringanExtra` R package](https://github.com/gadenbuie/xaringanExtra)
  
  - [`xaringanthemer` R packge](https://pkg.garrickadenbuie.com/xaringanthemer/index.html)
  
  - [Xaringan Gallery](https://xaringan.gallery/)
  
  - [`DT` R package for interactive tables](https://rstudio.github.io/DT/)


---
# GSU theme

- How to enable the gsu theme:

```md
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: ["gsu", "gsu-fonts"]
```

- The GSU theme for `Xaringan` presentation is suitable to work with a 16:9 aspect ratio

```md
nature:
  highlightStyle: github
  highlightLines: true
  countIncrementalSlides: false
  ratio: "16:9"
```

---
# GSU theme

- We can make `blockquotes` by calling `<gsu-blockquote-red>some texts</gsu-blockquote-red>`,
`<gsu-blockquote-blue>some texts</gsu-blockquote-blue>`, `<gsu-blockquote-alt>some texts</gsu-blockquote-alt>`

<gsu-blockquote-red>Lorem</gsu-blockquote> 


<gsu-blockquote-blue> Ipsum </gsu-blockquote-blue> 

<gsu-blockquote-alt> dolor </gsu-blockquote-alt>


- Highlight text using `**text**` like **this**

- Italic text using `*text*` like *this*

- Bold text using `.bold[text]` like .bold[text]

---
# GSU theme

- We can change the color of any text by using `.color[text]`. I prepared three color palettes for the users. Two of which using the `MetBrewer` packagke 

  - : `.gsu-blue[text]`,`.gsu-dark[text]`,`.gsu-gray-blue[text]`,`.gsu-gray-darker[text]`, `.gsu-gray-darkest[text]`, `.gsu-anchor-color[text]`
  - .gsu-blue[gsu blue], .gsu-dark[gsu dark], .gsu-gray-blue[gsu gray blue], .gsu-gray-darker[gsu gray darker], .gsu-gray-darkest[gsu gray darkest], .gsu-anchor-color[gsu anchor]

 - Hiroshige: .hiro-red[hiro red], .hiro-orange[hiro orange], .hiro-light-orange[Light Orange], .hiro-light-blue[light blue], .hiro-dark-blue[Dark Blue]

 - Veronese: .vero-red[Vero Red], .vero-brown[Vero Brown], .vero-yellow[Vero Yellow], .vero-teal[Vero Teal], .vero-blue[Vero Blue]

---
class: bold-last-item

# GSU theme

- add `class: bold-last-item` at the beginning of each slide to switch on the **Bold-Last-Item**

```css
---
class: bold-last-item
```
--
- For example
--
- Bullet list 1
--
- Bullet list 2
--
- Bullet list 3
---
class: highlight-last-item
# GSU theme
- add `class: highlight-last-item` at the beginning of each slide to switch on the **Highlight-Last-Item**
--
- For example
--
- Bullet list 1
--
- Bullet list 2
--
- Bullet list 3
---
```{r xaringan-extra-styles, echo=FALSE}
xaringanExtra::use_extra_styles(
  hover_code_line = TRUE,         #<<
  mute_unhighlighted_code = TRUE  #<<
)
```
# R code and plot output

```{r, fig.height=4.5, fig.width=9, fig.retina=2, fig.align='center', message=FALSE, warning=FALSE}
library("tidyverse")
cars %>% 
  ggplot(aes(x = dist, y = speed)) + 
  geom_point() + 
  geom_smooth(method = 'lm', formula = y ~ poly(x, 2)) + 
  theme_bw(base_size = 24) 
```

---
# Some Tips

- Do not forget to try the option **`yolo: true`** under **`xaringan::moon_reader`** in the YAML metadata of your R Markdown document. A picture of smiling Karl will be randomly insert in the slides.

- Use [`DT`](https://rstudio.github.io/DT/) for interactive tables.

- [`xaringanExtra` R package](https://github.com/gadenbuie/xaringanExtra) has many other additional and powerful features.

- Insert emoji by using [`emo`](https://github.com/hadley/emo) R package `r emo::ji("thinking")` `r emo::ji("laugh")` `r emo::ji("+1")`



- If you don't like the default font size and color, you can change them by using html syntax `<span style='font-size:55pt; color:#cc0033'> some text! </span>`

- If you want to change any elements of this theme, feel free to edit the source file as you like.

- The best way to learn about `Xaringan` is reading other people's source codes.

---



---
class: section, middle, center

.frame[
# In the beginning...

]
--

# I made A column

---



---

.pull-left[

> "In October, 1960, Dr. Goodall watched as a chimpanzee bent a twig, stripped off it leaves, and used it to “fish” termites from their nest. Up until her moment of discovery, the ability to make and use tools had been considered uniquely human."
> 
> [janegoodall.org](https://janegoodall.org/our-story/our-legacy-of-science/)

]




---


